---
title: "Non-stationary model selection"
author: "D. Greenberg, C. Wor, C. Holt, & B. Connors"
date: "12/12/2022"
output:
  html_document:
    collapsed: no
    fig_caption: yes
    highlight: espresso
    number_sections: yes
    smooth_scroll: yes
    theme: sandstone
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r load,  include=FALSE}
library(here);library(ggplot2);library(dplyr);library(cowplot);library(formattable);library(ggthemes);library(ggspatial);library(sf);library(rnaturalearth);library(rnaturalearthdata)
source(here('code','samEst code','stan_functions.R'))
source(here('code','samEst code','lfo_stan_functions.R'))
source(here('code','samEst code','util_functions.R'))
options(dplyr.summarise.inform = FALSE)
stock_dat<- read.csv(here('data','filtered datasets','salmon_productivity_compilation_aug2022.csv'))
stock_info<- read.csv(here('data','filtered datasets','all_stocks_info_aug2022.csv'))
#Remove stocks with less than 15 years of recruitment data
stock_info_filtered=subset(stock_info,n.years>=18) #242 stocks
stock_info_filtered$stock.name=gsub('/','_',stock_info_filtered$stock.name)
stock_info_filtered$stock.name=gsub('&','and',stock_info_filtered$stock.name)

stock_info_filtered$state=factor(stock_info_filtered$state,levels=c('OR','WA','BC','AK'))
stock_info_filtered$ocean.basin=factor(stock_info_filtered$ocean.basin,levels=c('WC','GOA','BS'))

stock_dat2=subset(stock_dat,stock.id %in% stock_info_filtered$stock.id)
length(unique(stock_dat2$stock.id)) #242

stock_dat2$logR_S=log(stock_dat2$recruits/stock_dat2$spawners)

```

```{r, plot colour schemes}

sp_cols=cbind(c("darkgray", "darkgreen", "darkblue","sienna","darkred"),c('Chinook','Chum','Coho','Pink','Sockeye'))

mod_col=cbind(c("azure4", "azure3", "cyan4","cadetblue3","deepskyblue4",'seagreen','olivedrab','darkgreen'),seq=1:8)

```

# Spawner-recruit time-series overview
The goal of this document is to examine model performance of various stationary and non-stationary spawner-recruitment model forms for 242 Pacific salmon spawner-recruit time-series spanning five species of anadramous Pacific salmon (Chinook, Chum, Coho, Pink, and Sockeye) spanning from Oregon to Alaska.

## Map of timeseries
```{r, ts map,warning=FALSE,fig.dim = c(10, 8)}
world <- ne_countries(scale = "medium", returnclass = "sf")

all_lat_lon = stock_info_filtered %>% group_by(lat,lon,species) %>% summarize(n=n(),.groups = 'keep')
all_lat_lon$lon=ifelse(all_lat_lon$lon>0,-all_lat_lon$lon,all_lat_lon$lon)
ll_p=subset(all_lat_lon,species=='Pink')
ll_ch=subset(all_lat_lon,species=='Chum')
ll_soc=subset(all_lat_lon,species=='Sockeye')
ll_coh=subset(all_lat_lon,species=='Coho')
ll_chi=subset(all_lat_lon,species=='Chinook')

ggplot(data = world) + 
  geom_sf(fill= 'antiquewhite') +  xlab("Longitude") + ylab("Latitude") +
  geom_point(data = ll_p, mapping = aes(x = lon, y = lat), color = "sienna", size = 2.2*log(ll_p$n+1), alpha = 0.7) +
  geom_point(data = ll_ch, mapping = aes(x = lon, y = lat), color = "darkgreen", size = 2.2*log(ll_ch$n+1), alpha = 0.7) +
  geom_point(data =  ll_soc, mapping = aes(x = lon, y = lat), color = "darkred", size = 2.2*log(ll_soc$n+1), alpha = 0.7) +
  geom_point(data =  ll_coh, mapping = aes(x = lon, y = lat), color = "darkblue", size = 2.2*log(ll_coh$n+1), alpha = 0.7) +
  geom_point(data = ll_chi, mapping = aes(x = lon, y = lat), color = "darkgray", size = 2.2*log(ll_chi$n+1), alpha = 0.7) +
    annotate(geom = 'text', x = -155, y = 54.5, label = 'Chinook', color = 'darkgray', size = 3) + 
  annotate(geom = 'text', x = -155, y = 53.5, label = 'Chum', color = 'darkgreen', size = 3) + 
  annotate(geom = 'text', x = -155, y = 52.5, label = 'Coho', color = 'darkblue', size = 3) + 
  annotate(geom = 'text', x = -155, y = 51.5, label = 'Pink', color = 'sienna', size = 3) + 
  annotate(geom = 'text', x = -155, y = 50.5, label = 'Sockeye', color = 'darkred', size = 3) + 
  annotate(geom = 'point', x = -145, y = 54, size = 2.2*log(1+1)) +
  annotate(geom = 'point', x = -145, y = 53, size = 2.2*log(3+1)) + 
  annotate(geom = 'point', x = -145, y = 51.5, size = 2.2*log(10+1)) + 
  annotate(geom = 'point', x = -145, y = 50, size = 2.2*log(20+1)) + 
  annotate(geom = 'text', x = -142, y = 54.8,label='n', size = 2.5) +
  annotate(geom = 'text', x = -142, y = 54,label='1', size = 2.5) +
  annotate(geom = 'text', x = -142, y = 53,label='3', size = 2.5) + 
  annotate(geom = 'text', x = -142, y = 51.5,label='10', size = 2.5) + 
  annotate(geom = 'text', x = -142, y = 50,label='20', size = 2.5) + 
  annotation_scale(location = 'bl', width_hint = 0.5) + 
  annotation_north_arrow(location = 'bl', which_north = 'true', pad_x = unit(0.35, 'in'), pad_y = unit(0.25, 'in'), style = north_arrow_fancy_orienteering) + 
  coord_sf(xlim = c(-170, -120), ylim = c(47, 72), expand = T) +
theme(panel.grid.major = element_line(color = gray(.5), linetype = 'dashed', size = 0.5), panel.background = element_rect(fill = 'lightblue'),legend.title = element_blank())

```

## Time-series by jurisdiction

```{r, ts by state}
sp_sum<- stock_info_filtered %>% group_by(species,state) %>% summarize(n=n(),.groups='keep')

ggplot(sp_sum, aes(fill=species, y=n, x=state))+
scale_fill_manual(values=sp_cols[match(levels(factor(sp_sum$species)),sp_cols[,2])])+ 
  geom_bar(position="stack", stat="identity") + theme_minimal() +
xlab('')+ylab('No. time-series')

```

## Time-series by ocean basin

```{r, ts by ocean}
sp_sum<- stock_info_filtered %>% group_by(species,ocean.basin) %>% summarize(n=n(),.groups='keep')

ggplot(sp_sum, aes(fill=species, y=n, x=ocean.basin))+
scale_fill_manual(values=sp_cols[match(levels(factor(sp_sum$species)),sp_cols[,2])])+ 
  geom_bar(position="stack", stat="identity") + theme_minimal() +
xlab('')+ylab('No. time-series')

```

## Time-series by length

```{r, ts length}
sp_sum<- stock_info_filtered %>% group_by(n.years,species) %>% summarize(n=n(),.groups='keep')

ggplot(sp_sum, aes(fill=species, y=n, x=n.years))+
scale_fill_manual(values=sp_cols[match(levels(factor(sp_sum$species)),sp_cols[,2])])+ 
  geom_bar(position="stack", stat="identity") + theme_minimal() +
xlab('')+ylab('No. time-series')

```

#Models

We fit three classes of spawner-recruitment models with 8 models in total, all building off the Ricker stock-recruitment curve:

+ Stationary models (Time-Invariant)
    1. Simple (model **1**):  
    
    $log(R_t/S_t) = \alpha - \beta*S_t + w_t$
    2. AR(1) (model **2**):  
    
    $log(R_t/S_t) = \alpha - \beta*S_t + w_t$  
    $w_t = \epsilon_t + \rho*\epsilon_{t-1}$  
    $w_t ~ N(0,\sigma)$                                                                          
+ Dynamic linear models (Time-Varying)
    3. Dynamic $\alpha$ (model **3**):  
    $log(R_t/S_t) = \alpha_t - \beta*S_t + w_t$  
    $\alpha_t = \alpha_{t-1} + v_{t}$  
    $v_t ~ N(0,\sigma_{\alpha})$  
    4. Dynamic $\beta$ (model **4**):  
    $log(R_t/S_t) = \alpha - \beta_t*S_t + w_t$  
    $\beta_t = \beta_{t-1} + v_{t}$   
    $v_t ~ N(0,\sigma_{\beta})$  
    5. Dynamic $\alpha$ and $\beta$ (model **5**)
    $log(R_t/S_t) = \alpha_t - \beta_t*S_t + w_t$
    $\beta_t = \beta_{t-1} + v_{t}$  
    $\beta_t = \beta_{t-1} + v_{t}$  
    $v_t ~ N(0,\sigma_{\beta})$ 
        
+ Regime shift (Hidden Markov) models (Time-Varying)
    6. $\alpha$ Regime (model **6**)
    $log(R_t/S_t) = \alpha_k - \beta*S_t + w_t$
    7. $\beta$ Regime (model **7**)
    $log(R_t/S_t) = \alpha - \beta_k*S_t + w_t$
    8. $\alpha$ and $\beta$ Regime (model **8**) 
    $log(R_t/S_t) = \alpha_k - \beta_k*S_t + w_t$

#Model selection

For each Pacific salmon spawner-recruit time-series we estimate each of these 8 models using either Stan or TMB. We compared the likelihoods of observing the data given each of these models, which are then used to estimate different model selection criteria. Likelihoods are calculated from the normal log predictive density function in all cases.

Broadly the model selection criteria fell into two categories: 'in-sample' likelihoods of the model fits and 'out-of-sample' likelihoods, where in the latter a portion of the dataset is omitted from the model fitting stage and likelihoods estimate out-of-sample prediction accuracy.

Choice of model selection criteria and data to include are important components. We will examine several to see how it changes our ultimate inferences.

# 'In-sample' Model selection

In this section, we examine various model selection criteria that are based on how well the retrospective observations are fit by predictions from each of the 8 model forms.

## Stan PSIS LOO-CV

Here we use the Pareto-smoothed approximate 'leave-one-out' cross-validation approach, a Bayesian equivalent to AIC (cite:), as implemented in the 'loo' R package.

### Top models 
```{r, model weights loo}
loo=read.csv(here('outputs','ms_rmd','stan_looic_table_stackweight.csv'))
loo$lat=round(loo$lat,2)
loo$lon=round(loo$lon,2)
table(loo$best_mod)
round(table(loo$best_mod)/nrow(loo),3)
```

```{r, loo model weights by pop, warning = FALSE}
sp = loo %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = loo %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

ggplot(sp, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Top-ranked model (Stan LOO-CV)")+
  geom_bar(position="stack", stat="identity",color='white') +
  geom_text(label=sp$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=14),axis.text=element_text(size=14),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))+
annotation_custom(grid::textGrob(sp1$n[1]), xmin = 1, xmax = 1, ymin = 1.03, ymax = 1.03)+
  annotation_custom(grid::textGrob(sp1$n[2]), xmin = 2, xmax = 2, ymin = 1.03, ymax = 1.03)+
    annotation_custom(grid::textGrob(sp1$n[3]), xmin = 3, xmax = 3, ymin = 1.03, ymax = 1.03)+
      annotation_custom(grid::textGrob(sp1$n[4]), xmin = 4, xmax = 4, ymin = 1.03, ymax = 1.03)+
       annotation_custom(grid::textGrob(sp1$n[5]), xmin = 5, xmax = 5, ymin = 1.03, ymax = 1.03)

```

### By jurisdiction

Top models broken down by state/province:

```{r,loo mod broken down by state }
sp_state = loo %>% group_by(state,species,best_mod) %>% summarize(n=n(),.groups='keep')
sp_state1 = loo %>% group_by(state,species) %>% summarize(n=n(),.groups='keep')
sp_state$prop = sp_state$n/sp_state1$n[match(paste(sp_state$state,sp_state$species,sep='_'),paste(sp_state1$state,sp_state1$species,sep='_'))]

sp_ak=subset(sp_state,state=='AK')
sp1_ak=subset(sp_state1,state=='AK')
sp_bc=subset(sp_state,state=='BC')
sp1_bc=subset(sp_state1,state=='BC')
sp_wa=subset(sp_state,state=='WA')
sp1_wa=subset(sp_state1,state=='WA')
sp_or=subset(sp_state,state=='OR')
sp1_or=subset(sp_state1,state=='OR')

or_pl=ggplot(sp_or, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_or$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Oregon")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_or$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_or$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_or$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)


wa_pl=ggplot(sp_wa, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_wa$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Washington")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_wa$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_wa$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_wa$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_wa$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_wa$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)



bc_pl=ggplot(sp_bc, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_bc$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("British Columbia")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_bc$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_bc$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_bc$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_bc$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_bc$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_bc$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

ak_pl=ggplot(sp_ak, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ak$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ak$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_ak$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_ak$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_ak$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_ak$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_ak$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

pg1=plot_grid(or_pl+ theme(legend.position="none"),
          wa_pl+ theme(legend.position="none"),
          bc_pl+ theme(legend.position="none"),
          ak_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

legend= get_legend(bc_pl)

plot_grid(pg1,legend,rel_widths = c(3,.5))

```


### By ocean basin

Top models broken down by ocean basin:

```{r, loo broken down by state and ocean basin}
sp_ocean = loo %>% group_by(ocean.basin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp_ocean1 = loo %>% group_by(ocean.basin,species) %>% summarize(n=n(),.groups='keep')
sp_ocean2 = loo %>% group_by(ocean.basin,best_mod) %>% summarize(n=n(),.groups='keep')
sp_ocean3 = loo %>% group_by(ocean.basin) %>% summarize(n=n())
sp_ocean$prop = sp_ocean$n/sp_ocean1$n[match(paste(sp_ocean$ocean.basin,sp_ocean$species,sep='_'),paste(sp_ocean1$ocean.basin,sp_ocean1$species,sep='_'))]
sp_ocean2$prop = sp_ocean2$n/sp_ocean3$n[match(paste(sp_ocean2$ocean.basin,sp_ocean2$species,sep='_'),paste(sp_ocean3$ocean.basin,sp_ocean3$species,sep='_'))]


sp_BS=subset(sp_ocean,ocean.basin=='BS')
sp1_BS=subset(sp_ocean1,ocean.basin=='BS')
sp_GOA=subset(sp_ocean,ocean.basin=='GOA')
sp1_GOA=subset(sp_ocean1,ocean.basin=='GOA')
sp_WC=subset(sp_ocean,ocean.basin=='WC')
sp1_WC=subset(sp_ocean1,ocean.basin=='WC')


WC_pl=ggplot(sp_WC, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_WC$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("West Coast")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_WC$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_WC$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_WC$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_WC$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_WC$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_WC$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


GOA_pl=ggplot(sp_GOA, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_GOA$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Gulf of Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_GOA$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_GOA$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_GOA$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_GOA$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_GOA$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_GOA$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


BS_pl=ggplot(sp_BS, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_BS$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Bering Sea")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_BS$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_BS$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_BS$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_BS$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_BS$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_BS$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

total_pl=ggplot(sp_ocean2, aes(fill=factor(best_mod), y=prop, x=ocean.basin))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ocean2$best_mod)),mod_col[,2])],name='Model')+
   ggtitle("Total")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ocean2$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
  annotation_custom(grid::textGrob(sum(sp1_BS$n),gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sum(sp1_GOA$n),gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sum(sp1_WC$n),gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)


legend= get_legend(WC_pl)

pg1=plot_grid(WC_pl+ theme(legend.position="none"),
          GOA_pl+ theme(legend.position="none"),
          BS_pl+ theme(legend.position="none"),
          total_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(pg1,legend,rel_widths = c(3,.5))

```

### By time-series length

```{r, loo by ts length}
loo$ts_length_bin=cut(
 stock_info_filtered$n.years,
  breaks = quantile(stock_info_filtered$n.years, seq(0,1,by=0.2)),
  labels = c('18-26','27-35','35-45','46-50','50+'))

loo_ts = loo %>% group_by(ts_length_bin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp = loo %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = loo %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

sp_18=subset(loo_ts,ts_length_bin=='18-26')
sp_27=subset(loo_ts,ts_length_bin=='27-35')
sp_35=subset(loo_ts,ts_length_bin=='35-45')
sp_45=subset(loo_ts,ts_length_bin=='46-50')
sp_50=subset(loo_ts,ts_length_bin=='50+')

pl_18=ggplot(sp_18, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_18$species)),sp_cols[,2])])+ 
  ggtitle("18 - 26 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_27=ggplot(sp_27, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_27$species)),sp_cols[,2])])+
  ggtitle("27 - 35 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_35=ggplot(sp_35, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_35$species)),sp_cols[,2])])+
  ggtitle("35 - 45 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_45=ggplot(sp_45, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_45$species)),sp_cols[,2])])+
  ggtitle("46 - 50 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_50=ggplot(sp_50, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_50$species)),sp_cols[,2])])+
  ggtitle("50+ years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

legend= get_legend(pl_18)

plot_grid(pl_18+ theme(legend.position="none"),
          pl_27+ theme(legend.position="none"),
          pl_35+ theme(legend.position="none"),
          pl_45+ theme(legend.position="none"),
          pl_50+ theme(legend.position="none"),
          legend,
          ncol=3,nrow=2,labels=c("A","B","C","D","E"))
```


## TMB AICc

### Top models
```{r, model weights AIC}
aic=read.csv(here('outputs','ms_rmd','aic_table.csv'))
aic$lat=round(aic$lat,2)
aic$lon=round(aic$lon,2)
table(aic$best_mod)
round(table(aic$best_mod)/nrow(aic),3)
```

```{r, AIC model weights by pop, warning = FALSE}
sp = aic %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = aic %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

mod_col=cbind(c("azure4", "azure3", "cyan4","cadetblue3","deepskyblue4",'seagreen','olivedrab','darkgreen'),seq=1:8)

ggplot(sp, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Top-ranked model (TMB AIC)")+
  geom_bar(position="stack", stat="identity",color='white') +
  geom_text(label=sp$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=14),axis.text=element_text(size=14),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))+
annotation_custom(grid::textGrob(sp1$n[1]), xmin = 1, xmax = 1, ymin = 1.03, ymax = 1.03)+
  annotation_custom(grid::textGrob(sp1$n[2]), xmin = 2, xmax = 2, ymin = 1.03, ymax = 1.03)+
    annotation_custom(grid::textGrob(sp1$n[3]), xmin = 3, xmax = 3, ymin = 1.03, ymax = 1.03)+
      annotation_custom(grid::textGrob(sp1$n[4]), xmin = 4, xmax = 4, ymin = 1.03, ymax = 1.03)+
       annotation_custom(grid::textGrob(sp1$n[5]), xmin = 5, xmax = 5, ymin = 1.03, ymax = 1.03)
```

### By jursidiction

Top models broken down by state:

```{r, AIC w broken down by state }
sp_state = aic %>% group_by(state,species,best_mod) %>% summarize(n=n(),.groups='keep')
sp_state1 = aic %>% group_by(state,species) %>% summarize(n=n(),.groups='keep')
sp_state$prop = sp_state$n/sp_state1$n[match(paste(sp_state$state,sp_state$species,sep='_'),paste(sp_state1$state,sp_state1$species,sep='_'))]

sp_ak=subset(sp_state,state=='AK')
sp1_ak=subset(sp_state1,state=='AK')
sp_bc=subset(sp_state,state=='BC')
sp1_bc=subset(sp_state1,state=='BC')
sp_wa=subset(sp_state,state=='WA')
sp1_wa=subset(sp_state1,state=='WA')
sp_or=subset(sp_state,state=='OR')
sp1_or=subset(sp_state1,state=='OR')

or_pl=ggplot(sp_or, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_or$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Oregon")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_or$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_or$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_or$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)


wa_pl=ggplot(sp_wa, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_wa$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Washington")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_wa$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_wa$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_wa$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_wa$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_wa$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)


bc_pl=ggplot(sp_bc, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_bc$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("British Columbia")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_bc$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_bc$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_bc$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_bc$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_bc$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_bc$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

ak_pl=ggplot(sp_ak, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ak$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ak$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_ak$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_ak$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_ak$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_ak$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_ak$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

pg1=plot_grid(or_pl+ theme(legend.position="none"),
          wa_pl+ theme(legend.position="none"),
          bc_pl+ theme(legend.position="none"),
          ak_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

legend= get_legend(bc_pl)

plot_grid(pg1,legend,rel_widths = c(3,.5))


```

### Ocean basins - TMB AIC

Top models broken down by ocean basin:

```{r, top AIC model broken down by state and ocean basin}
sp_ocean = aic %>% group_by(ocean.basin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp_ocean1 = aic %>% group_by(ocean.basin,species) %>% summarize(n=n(),.groups='keep')
sp_ocean2 = aic %>% group_by(ocean.basin,best_mod) %>% summarize(n=n(),.groups='keep')
sp_ocean3 = aic %>% group_by(ocean.basin) %>% summarize(n=n())
sp_ocean$prop = sp_ocean$n/sp_ocean1$n[match(paste(sp_ocean$ocean.basin,sp_ocean$species,sep='_'),paste(sp_ocean1$ocean.basin,sp_ocean1$species,sep='_'))]
sp_ocean2$prop = sp_ocean2$n/sp_ocean3$n[match(paste(sp_ocean2$ocean.basin,sp_ocean2$species,sep='_'),paste(sp_ocean3$ocean.basin,sp_ocean3$species,sep='_'))]


sp_BS=subset(sp_ocean,ocean.basin=='BS')
sp1_BS=subset(sp_ocean1,ocean.basin=='BS')
sp_GOA=subset(sp_ocean,ocean.basin=='GOA')
sp1_GOA=subset(sp_ocean1,ocean.basin=='GOA')
sp_WC=subset(sp_ocean,ocean.basin=='WC')
sp1_WC=subset(sp_ocean1,ocean.basin=='WC')


WC_pl=ggplot(sp_WC, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_WC$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("West Coast")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_WC$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_WC$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_WC$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_WC$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_WC$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_WC$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


GOA_pl=ggplot(sp_GOA, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_GOA$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Gulf of Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_GOA$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_GOA$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_GOA$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_GOA$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_GOA$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_GOA$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


BS_pl=ggplot(sp_BS, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_BS$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Bering Sea")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_BS$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_BS$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_BS$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_BS$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_BS$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_BS$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

total_pl=ggplot(sp_ocean2, aes(fill=factor(best_mod), y=prop, x=ocean.basin))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ocean2$best_mod)),mod_col[,2])],name='Model')+
   ggtitle("Total")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ocean2$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
  annotation_custom(grid::textGrob(sum(sp1_BS$n),gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sum(sp1_GOA$n),gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sum(sp1_WC$n),gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)


legend= get_legend(total_pl)

pg1=plot_grid(WC_pl+ theme(legend.position="none"),
          GOA_pl+ theme(legend.position="none"),
          BS_pl+ theme(legend.position="none"),
          total_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(pg1,legend,rel_widths = c(3,.5))
```

### By time-series length

```{r, aic by ts length}
aic$ts_length_bin=cut(
 stock_info_filtered$n.years,
  breaks = quantile(stock_info_filtered$n.years, seq(0,1,by=0.2)),
  labels = c('18-26','27-35','35-45','46-50','50+'))

aic_ts = aic %>% group_by(ts_length_bin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp = aic %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = aic %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

sp_18=subset(aic_ts,ts_length_bin=='18-26')
sp_27=subset(aic_ts,ts_length_bin=='27-35')
sp_35=subset(aic_ts,ts_length_bin=='35-45')
sp_45=subset(aic_ts,ts_length_bin=='46-50')
sp_50=subset(aic_ts,ts_length_bin=='50+')

pl_18=ggplot(sp_18, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_18$species)),sp_cols[,2])])+ 
  ggtitle("18 - 26 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_27=ggplot(sp_27, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_27$species)),sp_cols[,2])])+
  ggtitle("27 - 35 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_35=ggplot(sp_35, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_35$species)),sp_cols[,2])])+
  ggtitle("35 - 45 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_45=ggplot(sp_45, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_45$species)),sp_cols[,2])])+
  ggtitle("46 - 50 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_50=ggplot(sp_50, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_50$species)),sp_cols[,2])])+
  ggtitle("50+ years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

legend= get_legend(pl_18)

plot_grid(pl_18+ theme(legend.position="none"),
          pl_27+ theme(legend.position="none"),
          pl_35+ theme(legend.position="none"),
          pl_45+ theme(legend.position="none"),
          pl_50+ theme(legend.position="none"),
          legend,
          ncol=3,nrow=2,labels=c("A","B","C","D","E"))
```




## TMB BIC

### Top models
```{r, BIC model weights}
bic=read.csv(here('outputs','ms_rmd','aic_table.csv'))
bic$lat=round(bic$lat,2)
bic$lon=round(bic$lon,2)
table(bic$best_mod)
round(table(bic$best_mod)/nrow(bic),3)
```

```{r, BIC model weights by pop, warning = FALSE}

sp = bic %>% group_by(best_mod,species) %>% summarize(n=n())

ggplot(sp, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=c("darkgray", "darkgreen", "darkblue","darksalmon","darkred"))+ 
  ggtitle("Top-ranked model (TMB BIC)")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=14),axis.text=element_text(size=14),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))
```

### By jurisdiction

Top models broken down by state:

```{r, top model BIC broken down by state }
sp_state = bic %>% group_by(state,best_mod,species) %>% summarize(n=n())
sp_ak=subset(sp_state,state=='AK')
sp_bc=subset(sp_state,state=='BC')
sp_wa=subset(sp_state,state=='WA')
sp_or=subset(sp_state,state=='OR')

or_pl=ggplot(sp_or, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=c("darkgray", "darkgreen", "darkblue","darksalmon","darkred"))+ 
  ggtitle("Oregon")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

wa_pl=ggplot(sp_wa, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=c("darkgray", "darkgreen", "darkblue","darksalmon","darkred"))+
  ggtitle("Washington")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

bc_pl=ggplot(sp_bc, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=c("darkgray", "darkgreen", "darkblue","darksalmon","darkred"))+
  ggtitle("British Columbia")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

ak_pl=ggplot(sp_ak, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=c("darkgray", "darkgreen", "darkblue","darksalmon","darkred"))+
  ggtitle("Alaska")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))


pg1=plot_grid(or_pl+ theme(legend.position="none"),
          wa_pl+ theme(legend.position="none"),
          bc_pl+ theme(legend.position="none"),
          ak_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

legend= get_legend(bc_pl)

plot_grid(pg1,legend,rel_widths = c(3,.5))

```


### By ocean basin

Top models broken down by ocean basin:

```{r, top model BIC broken down by ocean basin}
sp_ocean = bic %>% group_by(ocean.basin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp_ocean1 = bic %>% group_by(ocean.basin,species) %>% summarize(n=n(),.groups='keep')
sp_ocean2 = bic %>% group_by(ocean.basin,best_mod) %>% summarize(n=n(),.groups='keep')
sp_ocean3 = bic %>% group_by(ocean.basin) %>% summarize(n=n())
sp_ocean$prop = sp_ocean$n/sp_ocean1$n[match(paste(sp_ocean$ocean.basin,sp_ocean$species,sep='_'),paste(sp_ocean1$ocean.basin,sp_ocean1$species,sep='_'))]
sp_ocean2$prop = sp_ocean2$n/sp_ocean3$n[match(paste(sp_ocean2$ocean.basin,sp_ocean2$species,sep='_'),paste(sp_ocean3$ocean.basin,sp_ocean3$species,sep='_'))]


sp_BS=subset(sp_ocean,ocean.basin=='BS')
sp1_BS=subset(sp_ocean1,ocean.basin=='BS')
sp_GOA=subset(sp_ocean,ocean.basin=='GOA')
sp1_GOA=subset(sp_ocean1,ocean.basin=='GOA')
sp_WC=subset(sp_ocean,ocean.basin=='WC')
sp1_WC=subset(sp_ocean1,ocean.basin=='WC')


WC_pl=ggplot(sp_WC, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_WC$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("West Coast")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_WC$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_WC$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_WC$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_WC$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_WC$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_WC$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


GOA_pl=ggplot(sp_GOA, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_GOA$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Gulf of Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_GOA$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_GOA$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_GOA$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_GOA$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_GOA$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_GOA$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


BS_pl=ggplot(sp_BS, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_BS$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Bering Sea")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_BS$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_BS$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_BS$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_BS$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_BS$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_BS$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

total_pl=ggplot(sp_ocean2, aes(fill=factor(best_mod), y=prop, x=ocean.basin))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ocean2$best_mod)),mod_col[,2])],name='Model')+
   ggtitle("Total")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ocean2$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
  annotation_custom(grid::textGrob(sum(sp1_BS$n),gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sum(sp1_GOA$n),gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sum(sp1_WC$n),gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)


legend= get_legend(total_pl)

pg1=plot_grid(WC_pl+ theme(legend.position="none"),
          GOA_pl+ theme(legend.position="none"),
          BS_pl+ theme(legend.position="none"),
          total_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(pg1,legend,rel_widths = c(3,.5))
```

### By time-series length

```{r, bic by ts length}
bic$ts_length_bin=cut(
 stock_info_filtered$n.years,
  breaks = quantile(stock_info_filtered$n.years, seq(0,1,by=0.2)),
  labels = c('18-26','27-35','35-45','46-50','50+'))

bic_ts = bic %>% group_by(ts_length_bin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp = bic %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = bic %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

sp_18=subset(bic_ts,ts_length_bin=='18-26')
sp_27=subset(bic_ts,ts_length_bin=='27-35')
sp_35=subset(bic_ts,ts_length_bin=='35-45')
sp_45=subset(bic_ts,ts_length_bin=='46-50')
sp_50=subset(bic_ts,ts_length_bin=='50+')

pl_18=ggplot(sp_18, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_18$species)),sp_cols[,2])])+ 
  ggtitle("18 - 26 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_27=ggplot(sp_27, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_27$species)),sp_cols[,2])])+
  ggtitle("27 - 35 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_35=ggplot(sp_35, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_35$species)),sp_cols[,2])])+
  ggtitle("35 - 45 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_45=ggplot(sp_45, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_45$species)),sp_cols[,2])])+
  ggtitle("46 - 50 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_50=ggplot(sp_50, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_50$species)),sp_cols[,2])])+
  ggtitle("50+ years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

legend= get_legend(pl_18)

plot_grid(pl_18+ theme(legend.position="none"),
          pl_27+ theme(legend.position="none"),
          pl_35+ theme(legend.position="none"),
          pl_45+ theme(legend.position="none"),
          pl_50+ theme(legend.position="none"),
          legend,
          ncol=3,nrow=2,labels=c("A","B","C","D","E"))
```


# 'Out-of-sample' Model selection

In leave-future-out cross-validation, we iteratively fit models to historical data (starting from a minimum sample window, $L$, and estimate the ability of each model to predict out-of-sample estimates 1-year ahead. Likelihoods for each observation are estimated from the Normal log predictive density function based on the expectation for each model. This is repeated for all observations from $L+1:N$. 

## Stan LFO-CV (L = 2/3n)

Note the minimum training set here is set to 2/3rds of the total observations, this will ultimately be changed to $L = 10$ (it is very slow to estimate). 

### Top models

```{r, model weights lfo}
lfo=read.csv(here('outputs','ms_rmd','lfo_table.csv'))
lfo$lat=round(lfo$lat,2)
lfo$lon=round(lfo$lon,2)
table(lfo$best_mod)
round(table(lfo$best_mod)/nrow(lfo),3)
```
```{r, model weights by pop, warning = FALSE}

sp = lfo %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = lfo %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

mod_col=cbind(c("azure4", "azure3", "cyan4","cadetblue3","deepskyblue4",'seagreen','olivedrab','darkgreen'),seq=1:8)

ggplot(sp, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Top-ranked model (Stan LFO-CV, L=2/3n)")+
  geom_bar(position="stack", stat="identity",color='white') +
  geom_text(label=sp$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=14),axis.text=element_text(size=14),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))+
annotation_custom(grid::textGrob(sp1$n[1]), xmin = 1, xmax = 1, ymin = 1.03, ymax = 1.03)+
  annotation_custom(grid::textGrob(sp1$n[2]), xmin = 2, xmax = 2, ymin = 1.03, ymax = 1.03)+
    annotation_custom(grid::textGrob(sp1$n[3]), xmin = 3, xmax = 3, ymin = 1.03, ymax = 1.03)+
      annotation_custom(grid::textGrob(sp1$n[4]), xmin = 4, xmax = 4, ymin = 1.03, ymax = 1.03)+
       annotation_custom(grid::textGrob(sp1$n[5]), xmin = 5, xmax = 5, ymin = 1.03, ymax = 1.03)
```

### By jurisdiction

Top models broken down by state:

```{r, broken down by state }
sp_state = lfo %>% group_by(state,species,best_mod) %>% summarize(n=n(),.groups='keep')
sp_state1 = lfo %>% group_by(state,species) %>% summarize(n=n(),.groups='keep')
sp_state$prop = sp_state$n/sp_state1$n[match(paste(sp_state$state,sp_state$species,sep='_'),paste(sp_state1$state,sp_state1$species,sep='_'))]

sp_ak=subset(sp_state,state=='AK')
sp1_ak=subset(sp_state1,state=='AK')
sp_bc=subset(sp_state,state=='BC')
sp1_bc=subset(sp_state1,state=='BC')
sp_wa=subset(sp_state,state=='WA')
sp1_wa=subset(sp_state1,state=='WA')
sp_or=subset(sp_state,state=='OR')
sp1_or=subset(sp_state1,state=='OR')

or_pl=ggplot(sp_or, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_or$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Oregon")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_or$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_or$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_or$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)


wa_pl=ggplot(sp_wa, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_wa$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Washington")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_wa$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_wa$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_wa$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_wa$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_wa$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)



bc_pl=ggplot(sp_bc, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_bc$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("British Columbia")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_bc$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_bc$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_bc$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_bc$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_bc$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_bc$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

ak_pl=ggplot(sp_ak, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ak$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ak$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_ak$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_ak$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_ak$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_ak$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_ak$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

pg1=plot_grid(or_pl+ theme(legend.position="none"),
          wa_pl+ theme(legend.position="none"),
          bc_pl+ theme(legend.position="none"),
          ak_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

legend= get_legend(bc_pl)

plot_grid(pg1,legend,rel_widths = c(3,.5))

```


### By ocean basin

Top models broken down by ocean basin:

```{r, broken down by state and ocean basin}
sp_ocean = lfo %>% group_by(ocean.basin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp_ocean1 = lfo %>% group_by(ocean.basin,species) %>% summarize(n=n(),.groups='keep')
sp_ocean2 = lfo %>% group_by(ocean.basin,best_mod) %>% summarize(n=n(),.groups='keep')
sp_ocean3 = lfo %>% group_by(ocean.basin) %>% summarize(n=n())
sp_ocean$prop = sp_ocean$n/sp_ocean1$n[match(paste(sp_ocean$ocean.basin,sp_ocean$species,sep='_'),paste(sp_ocean1$ocean.basin,sp_ocean1$species,sep='_'))]
sp_ocean2$prop = sp_ocean2$n/sp_ocean3$n[match(paste(sp_ocean2$ocean.basin,sp_ocean2$species,sep='_'),paste(sp_ocean3$ocean.basin,sp_ocean3$species,sep='_'))]


sp_BS=subset(sp_ocean,ocean.basin=='BS')
sp1_BS=subset(sp_ocean1,ocean.basin=='BS')
sp_GOA=subset(sp_ocean,ocean.basin=='GOA')
sp1_GOA=subset(sp_ocean1,ocean.basin=='GOA')
sp_WC=subset(sp_ocean,ocean.basin=='WC')
sp1_WC=subset(sp_ocean1,ocean.basin=='WC')


WC_pl=ggplot(sp_WC, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_WC$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("West Coast")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_WC$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_WC$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_WC$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_WC$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_WC$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_WC$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


GOA_pl=ggplot(sp_GOA, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_GOA$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Gulf of Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_GOA$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_GOA$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_GOA$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_GOA$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_GOA$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_GOA$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


BS_pl=ggplot(sp_BS, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_BS$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Bering Sea")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_BS$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_BS$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_BS$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_BS$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_BS$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_BS$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

total_pl=ggplot(sp_ocean2, aes(fill=factor(best_mod), y=prop, x=ocean.basin))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ocean2$best_mod)),mod_col[,2])],name='Model')+
   ggtitle("Total")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ocean2$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
  annotation_custom(grid::textGrob(sum(sp1_BS$n),gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sum(sp1_GOA$n),gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sum(sp1_WC$n),gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)


legend= get_legend(GOA_pl)

pg1=plot_grid(WC_pl+ theme(legend.position="none"),
          GOA_pl+ theme(legend.position="none"),
          BS_pl+ theme(legend.position="none"),
          total_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(pg1,legend,rel_widths = c(3,.5))



```

### By time-series length

```{r, lfo by ts length}
lfo$ts_length_bin=cut(
 stock_info_filtered$n.years,
  breaks = quantile(stock_info_filtered$n.years, seq(0,1,by=0.2)),
  labels = c('18-26','27-35','35-45','46-50','50+'))

lfo_ts = lfo %>% group_by(ts_length_bin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp = lfo %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = lfo %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

sp_18=subset(lfo_ts,ts_length_bin=='18-26')
sp_27=subset(lfo_ts,ts_length_bin=='27-35')
sp_35=subset(lfo_ts,ts_length_bin=='35-45')
sp_45=subset(lfo_ts,ts_length_bin=='46-50')
sp_50=subset(lfo_ts,ts_length_bin=='50+')

pl_18=ggplot(sp_18, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_18$species)),sp_cols[,2])])+ 
  ggtitle("18 - 26 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_27=ggplot(sp_27, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_27$species)),sp_cols[,2])])+
  ggtitle("27 - 35 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_35=ggplot(sp_35, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_35$species)),sp_cols[,2])])+
  ggtitle("35 - 45 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_45=ggplot(sp_45, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_45$species)),sp_cols[,2])])+
  ggtitle("46 - 50 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_50=ggplot(sp_50, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_50$species)),sp_cols[,2])])+
  ggtitle("50+ years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

legend= get_legend(pl_18)

plot_grid(pl_18+ theme(legend.position="none"),
          pl_27+ theme(legend.position="none"),
          pl_35+ theme(legend.position="none"),
          pl_45+ theme(legend.position="none"),
          pl_50+ theme(legend.position="none"),
          legend,
          ncol=3,nrow=2,labels=c("A","B","C","D","E"))
```



## TMB LFO-CV (L=10)

Note the minimum training set here is $L = 10$. 

### Top models

```{r, TMB lfo model weights}
tmb_lfo=read.csv(here('outputs','ms_rmd','tmb_lfo_table.csv'))
tmb_lfo$lat=round(tmb_lfo$lat,2)
tmb_lfo$lon=round(tmb_lfo$lon,2)
table(tmb_lfo$best_mod)
round(table(tmb_lfo$best_mod)/nrow(tmb_lfo),3)
```
```{r, TMB lfo model weights by pop, warning = FALSE}
sp = tmb_lfo %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = tmb_lfo %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

mod_col=cbind(c("azure4", "azure3", "cyan4","cadetblue3","deepskyblue4",'seagreen','olivedrab','darkgreen'),seq=1:8)

ggplot(sp, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Top-ranked model (TMB LFO-CV, L = 10)")+
  geom_bar(position="stack", stat="identity",color='white') +
  geom_text(label=sp$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=14),axis.text=element_text(size=14),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))+
annotation_custom(grid::textGrob(sp1$n[1]), xmin = 1, xmax = 1, ymin = 1.03, ymax = 1.03)+
  annotation_custom(grid::textGrob(sp1$n[2]), xmin = 2, xmax = 2, ymin = 1.03, ymax = 1.03)+
    annotation_custom(grid::textGrob(sp1$n[3]), xmin = 3, xmax = 3, ymin = 1.03, ymax = 1.03)+
      annotation_custom(grid::textGrob(sp1$n[4]), xmin = 4, xmax = 4, ymin = 1.03, ymax = 1.03)+
       annotation_custom(grid::textGrob(sp1$n[5]), xmin = 5, xmax = 5, ymin = 1.03, ymax = 1.03)
```

### By jurisdiction

Top models broken down by state:

```{r, TMB lfo top mod broken down by state }
sp_state = tmb_lfo %>% group_by(state,species,best_mod) %>% summarize(n=n(),.groups='keep')
sp_state1 = tmb_lfo %>% group_by(state,species) %>% summarize(n=n(),.groups='keep')
sp_state$prop = sp_state$n/sp_state1$n[match(paste(sp_state$state,sp_state$species,sep='_'),paste(sp_state1$state,sp_state1$species,sep='_'))]

sp_ak=subset(sp_state,state=='AK')
sp1_ak=subset(sp_state1,state=='AK')
sp_bc=subset(sp_state,state=='BC')
sp1_bc=subset(sp_state1,state=='BC')
sp_wa=subset(sp_state,state=='WA')
sp1_wa=subset(sp_state1,state=='WA')
sp_or=subset(sp_state,state=='OR')
sp1_or=subset(sp_state1,state=='OR')

or_pl=ggplot(sp_or, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_or$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Oregon")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_or$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_or$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_or$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)


wa_pl=ggplot(sp_wa, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_wa$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Washington")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_wa$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_wa$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_wa$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_wa$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_wa$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)


bc_pl=ggplot(sp_bc, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_bc$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("British Columbia")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_bc$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_bc$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_bc$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_bc$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_bc$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_bc$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

ak_pl=ggplot(sp_ak, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ak$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ak$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_ak$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_ak$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_ak$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_ak$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_ak$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

pg1=plot_grid(or_pl+ theme(legend.position="none"),
          wa_pl+ theme(legend.position="none"),
          bc_pl+ theme(legend.position="none"),
          ak_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

legend= get_legend(bc_pl)

plot_grid(pg1,legend,rel_widths = c(3,.5))


```


### By ocean basin

Top models broken down by ocean basin:

```{r, TMB lfo top mod broken down by state and ocean basin}
sp_ocean = tmb_lfo %>% group_by(ocean.basin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp_ocean1 = tmb_lfo %>% group_by(ocean.basin,species) %>% summarize(n=n(),.groups='keep')
sp_ocean2 = tmb_lfo %>% group_by(ocean.basin,best_mod) %>% summarize(n=n(),.groups='keep')
sp_ocean3 = tmb_lfo %>% group_by(ocean.basin) %>% summarize(n=n())
sp_ocean$prop = sp_ocean$n/sp_ocean1$n[match(paste(sp_ocean$ocean.basin,sp_ocean$species,sep='_'),paste(sp_ocean1$ocean.basin,sp_ocean1$species,sep='_'))]
sp_ocean2$prop = sp_ocean2$n/sp_ocean3$n[match(paste(sp_ocean2$ocean.basin,sp_ocean2$species,sep='_'),paste(sp_ocean3$ocean.basin,sp_ocean3$species,sep='_'))]


sp_BS=subset(sp_ocean,ocean.basin=='BS')
sp1_BS=subset(sp_ocean1,ocean.basin=='BS')
sp_GOA=subset(sp_ocean,ocean.basin=='GOA')
sp1_GOA=subset(sp_ocean1,ocean.basin=='GOA')
sp_WC=subset(sp_ocean,ocean.basin=='WC')
sp1_WC=subset(sp_ocean1,ocean.basin=='WC')


WC_pl=ggplot(sp_WC, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_WC$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("West Coast")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_WC$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_WC$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_WC$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_WC$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_WC$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_WC$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


GOA_pl=ggplot(sp_GOA, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_GOA$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Gulf of Alaska")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_GOA$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_GOA$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_GOA$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_GOA$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_GOA$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_GOA$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)


BS_pl=ggplot(sp_BS, aes(fill=factor(best_mod), y=prop, x=species))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_BS$best_mod)),mod_col[,2])],name='Model')+ 
  ggtitle("Bering Sea")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_BS$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
annotation_custom(grid::textGrob(sp1_BS$n[1],gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sp1_BS$n[2],gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sp1_BS$n[3],gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)+
      annotation_custom(grid::textGrob(sp1_BS$n[4],gp=grid::gpar(fontsize=8)), xmin = 4, xmax = 4, ymin = 1.05, ymax = 1.05)+
         annotation_custom(grid::textGrob(sp1_BS$n[5],gp=grid::gpar(fontsize=8)), xmin = 5, xmax = 5, ymin = 1.05, ymax = 1.05)

total_pl=ggplot(sp_ocean2, aes(fill=factor(best_mod), y=prop, x=ocean.basin))+
  scale_fill_manual(values=mod_col[match(levels(factor(sp_ocean2$best_mod)),mod_col[,2])],name='Model')+
   ggtitle("Total")+
  geom_bar(position="stack", stat="identity") +
  geom_text(label=sp_ocean2$n, position = position_stack(vjust = 0.5),colour='white',size=2.2)+
  ylim(0,1.05)+
  theme_minimal() +
  xlab('')+
  ylab('Prop. populations')+ 
  theme(text=element_text(size=10),axis.text=element_text(size=10),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=12))+
  annotation_custom(grid::textGrob(sum(sp1_BS$n),gp=grid::gpar(fontsize=8)), xmin = 1, xmax = 1, ymin = 1.05, ymax = 1.05)+
  annotation_custom(grid::textGrob(sum(sp1_GOA$n),gp=grid::gpar(fontsize=8)), xmin = 2, xmax = 2, ymin = 1.05, ymax = 1.05)+
    annotation_custom(grid::textGrob(sum(sp1_WC$n),gp=grid::gpar(fontsize=8)), xmin = 3, xmax = 3, ymin = 1.05, ymax = 1.05)


legend= get_legend(total_pl)

pg1=plot_grid(WC_pl+ theme(legend.position="none"),
          GOA_pl+ theme(legend.position="none"),
          BS_pl+ theme(legend.position="none"),
          total_pl+ theme(legend.position="none"),
          ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(pg1,legend,rel_widths = c(3,.5))


```

### By time-series length

```{r, tmb lfo by ts length}
tmb_lfo$ts_length_bin=cut(
 stock_info_filtered$n.years,
  breaks = quantile(stock_info_filtered$n.years, seq(0,1,by=0.2)),
  labels = c('18-26','27-35','35-45','46-50','50+'))

tmb_lfo_ts = tmb_lfo %>% group_by(ts_length_bin,best_mod,species) %>% summarize(n=n(),.groups='keep')
sp = tmb_lfo %>% group_by(species,best_mod) %>% summarize(n=n(),.groups='keep')
sp1 = tmb_lfo %>% group_by(species) %>% summarize(n=n())
sp$prop = sp$n/sp1$n[match(sp$species,sp1$species)]

sp_18=subset(tmb_lfo_ts,ts_length_bin=='18-26')
sp_27=subset(tmb_lfo_ts,ts_length_bin=='27-35')
sp_35=subset(tmb_lfo_ts,ts_length_bin=='35-45')
sp_45=subset(tmb_lfo_ts,ts_length_bin=='46-50')
sp_50=subset(tmb_lfo_ts,ts_length_bin=='50+')

pl_18=ggplot(sp_18, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_18$species)),sp_cols[,2])])+ 
  ggtitle("18 - 26 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_27=ggplot(sp_27, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_27$species)),sp_cols[,2])])+
  ggtitle("27 - 35 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
  xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12),axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_35=ggplot(sp_35, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_35$species)),sp_cols[,2])])+
  ggtitle("35 - 45 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_45=ggplot(sp_45, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_45$species)),sp_cols[,2])])+
  ggtitle("46 - 50 years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('No. populations')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

pl_50=ggplot(sp_50, aes(fill=species, y=n, x=factor(best_mod)))+
  scale_fill_manual(values=sp_cols[match(levels(factor(sp_50$species)),sp_cols[,2])])+
  ggtitle("50+ years")+
  geom_bar(position="stack", stat="identity") + 
  theme_minimal() +
   xlim(factor(seq(1:8)))+
  xlab('')+
  ylab('')+ 
  theme(text=element_text(size=12), axis.title=element_text(size=12,face="bold"),axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),plot.title = element_text(size=14))

legend= get_legend(pl_18)

plot_grid(pl_18+ theme(legend.position="none"),
          pl_27+ theme(legend.position="none"),
          pl_35+ theme(legend.position="none"),
          pl_45+ theme(legend.position="none"),
          pl_50+ theme(legend.position="none"),
          legend,
          ncol=3,nrow=2,labels=c("A","B","C","D","E"))
```

# Population Overview

Here you will find the weights for each forms of the spawner-recruit model for every population. These are ordered by species and latitude of the point of ocean entry. The red shading indicates higher levels of weight towards a particular model.

## Stan PSIS LOO-CV

```{r, loo table}
formattable(loo[,2:ncol(loo)],
            list(area(col = 7:14) ~ color_tile("transparent", "red")))

```

## TMB AICc

```{r, AIC table}
formattable(aic[,2:ncol(aic)],
            list(area(col = 7:14) ~ color_tile("transparent", "red")))

```

## TMB BIC

```{r, BIC table}
formattable(bic[,2:ncol(bic)],
            list(area(col = 7:14) ~ color_tile("transparent", "red")))

```


## Stan LFO (L = 2/3n)

By population, ordered by species and latitude of ocean entry, with weights for the predictive accuracy of each model. Red indicates higher weight.

```{r, lfo table}
formattable(lfo[,2:ncol(lfo)],
            list(area(col = 7:14) ~ color_tile("transparent", "red")))

```

## TMB LFO-CV (L = 10)

```{r, tmb lfo table}
formattable(tmb_lfo[,2:ncol(tmb_lfo)],
            list(area(col = 7:14) ~ color_tile("transparent", "red")))

```
# S-R Plots
